---
title: "Investigate Exponential Dist. against Central Limit Theorem"
author: "Klevin D."
date: "February 22, 2016"
output: html_document
---

Synopsis
--------
This document investigates the exponential distribution in R and compares it with Central Limit Theorem. The distribution of averages of 40 exponentials will be evaluated. The distribution of averages looks far more Gaussian than the original exponential distribution.

Simulation
The code below creates necessary data with 1000 simulations.  
```{r}
mns = NULL
lamda <- 0.2
n <- 40
for (i in 1 : 1000) mns = c(mns, mean(rexp(n, rate = lamda)))
```

Plotting simulated data
```{r}
hist(mns)
```

Comparing Sample Mean
```{r}
sam_mean <- mean(mns)
th_mean <- 1/lamda
```
Sample Mean of exponential distribution : `r sam_mean`  
Theoritical Mean of exponential distribution : `r th_mean`  

Comparing Variance
```{r}
sam_var <- var(mns)
th_var <- (1/lamda)^2/n
```
Sample variance of distribution : `r sam_var`  
Theoritical variance of distribution : `r th_var`  

Checking for normality
```{r}
qqnorm(mns)
qqline(mns)
```

