---
title: "Investigate Exponential Dist. against Central Limit Theorem"
author: "Klevin D."
date: "February 22, 2016"
output: html_document
---

Synopsis
--------
This document investigates the exponential distribution in R and compares it with Central Limit Theorem. The distribution of averages of 40 exponentials will be evaluated. The distribution of averages looks far more Gaussian than the original exponential distribution.

Simulation
----------
The code below creates necessary data with 1000 simulations.  
```{r}
mns = NULL
lamda <- 0.2
n <- 40
for (i in 1 : 1000) mns = c(mns, mean(rexp(n, rate = lamda)))
```

Plotting simulated data
```{r}
hist(mns)
```

###Comparing Sample Mean
```{r}
sam_mean <- mean(mns)
th_mean <- 1/lamda
```
Sample Mean of exponential distribution : `r sam_mean`  
Theoretical Mean of exponential distribution : `r th_mean`  
This implies that mean of distribution of sample means is very close to theoretical mean of exponential distribution with lamda = 0.2.  

###Comparing Variance
```{r}
sam_var <- var(mns)
th_var <- (1/lamda)^2/n
```
Sample variance of distribution : `r sam_var`  
Theoretical variance of distribution : `r th_var`  
This implies that variance of distribution of sample means is very close to theoretical variance of exponential distribution with lamda = 0.2.  

###Checking for normality
To check whether the distribution on sample means is normal we will plot the q-q graph.
```{r}
qqnorm(mns)
qqline(mns, col="red")
```

The theoretical quantiles match the sample quantiles closely. This proves that the distribution is approximately normal.
