---
title: "ToothGrowth"
author: "Klevin D."
date: "February 23, 2016"
output: html_document
---

Synopsis
--------
This report analyses the effect of vitamin C on ToothGrowth using the ToothGrowth data in the R data sets package. The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

Load the ToothGrowth data
```{r}
data("ToothGrowth")
str(ToothGrowth)
```

Provide a basic summary of the data.
```{r}
summary(ToothGrowth)
```
Converting dose to factor variable since its a catergorical data.
```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

##Exploratory Data Analysis
```{r}
library(ggplot2)
ggplot(data = ToothGrowth, aes(x=dose, y=len)) + geom_boxplot(aes(fill=dose)) + facet_grid(.~supp)

```

Based on above plot, we can conclude that the dose has an effect on tooth growth. Supplement OJ seems to have more influence on toothgrowth compared to VC.


##Inferential Analysis
###Compare tooth growth by supp
Check for variance before t-test
```{r}
suppvar <- split(ToothGrowth$len, ToothGrowth$supp)
sapply(suppvar, var)
```
Based on the variance values, we will consider unequal variances.

Conducting t-test for influence of supp. 
```{r}
t.test(len~supp, data = ToothGrowth, paired=FALSE, var.equal=FALSE)
```
We observe p-value is greater than 0.05 and 95% confidence interval includes 0, thus we fail to reject null hypothesis that tooth growth is influenced by supp.

###Compare tooth growth by dose
Check for variance before t-test
```{r}
dosevar <- split(ToothGrowth$len, ToothGrowth$dose)
sapply(dosevar, var)
```
Based on the variance values, we will consider approximatey equal variances.

Conducting t-test for influence of dose. 
Dose 0.5 vs Dose 1
```{r}
with(data = ToothGrowth,
     t.test(len[dose==0.5], len[dose==1], paired=FALSE, var.equal=TRUE))
```
The p-value is approx. 0 and confidence interval does not contain 0. 

Dose 1 vs Dose 2
```{r}
with(data = ToothGrowth,
     t.test(len[dose==1], len[dose==2], paired=FALSE, var.equal=TRUE))
```
The p-value is approx. 0 and confidence interval does not contain 0. 


